---
title: "DataViz Exercises"
description: |
  Working through the week 3 interactive/tutorial of HDAT9800
author:
  - name: Shane Donohoe
    url: https://shndon.github.io/shane-explores-some-data-science/
date: 06-17-2021
draft: false
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
```

We are following some example work from https://r4ds.had.co.nz/data-visualisation.html

Because of time I'm not going to recreate much of the text from that chapter.

```{r}
head(mpg)
```



```{r}
mpg %>% 
  ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy))

```

Some ways to check dimensions / check out the dataset

```{r}
nrow(mpg)
ncol(mpg)
str(mpg)
dim(mpg)
mpg %>% glimpse
```


What does `drv` contain? 

```{r}

# ?mpg

```

```{r}

mpg %>% ggplot() +
  geom_point(aes(x = cyl, y = hwy))

```

```{r}

mpg %>% ggplot() +
  geom_point(aes(x = drv, y = class), position = "jitter")



```

```{r}
mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, colour = class), position = "jitter")



# notice how this one looks ... unhelpful


mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, size = class), position = "jitter")

mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, alpha = class), position = "jitter")

mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, shape = class), position = "jitter")

mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy), alpha = 0.3, position = "jitter")

mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, colour = cty, shape = class), position = "jitter")


mpg %>% ggplot() +
  geom_point(aes(x = displ, y = hwy, stroke = displ), position = "jitter")
```


Facetting

```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 6)


ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

```

```{r}
mpg %>% 
  ggplot(mapping = aes(x = displ, y = hwy, colour = drv)) +
  geom_smooth(mapping = aes(linetype = drv)) +
  geom_point()

```


(skipping over a bunch of examples and exercises)

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut))
```

Behind the scenes, `geom_bar` is creating `count` to be the y axis.


Lots of other good info in that chapter and the book generally. Check it out!







Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


